Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-16 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
更新表格

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|ccccccccccccccccc}
\toprule
Iterations &  0    &  1    &  2    &  4    & 8   & 16  & 32  & 64  & 128 & 256  & 512   & 1024  & 2048  & 4096  & 8192  & 16384 & 32768 \\ \midrule
AO (FGT)   & 0.004 & 0.002 &0.002 & 0.002 &0.002&0.002&0.003&0.007&0.042& 0.299& 0.668 & 0.746 & 0.781 & 0.798 & 0.820 & 0.821 & 0.818 \\
SR (FGT) & 0.000 & 0.000 &0.000 & 0.000 &0.000&0.000&0.001&0.005&0.044& 0.335& 0.749 & 0.822 & 0.855 & 0.872 & 0.895 & 0.897 & 0.890 \\ \midrule
AO (GT)    &  0.760& 0.757 &0.756 & 0.757 &0.757&0.758&0.759&0.753&0.720& 0.474& 0.150 & 0.095 & 0.071 & 0.041 & 0.032 & 0.032 & 0.035 \\
SR (GT) &  0.897& 0.894 &0.891 & 0.893 &0.891&0.893&0.896&0.888&0.852& 0.559& 0.164 & 0.098 & 0.066 & 0.031 & 0.021 & 0.022 & 0.023 \\ \midrule
SSIM     &  1.00 & 1.00  & 1.00 & 1.00  &1.00 &0.99 & 0.99& 0.97& 0.93& 0.86 & 0.86  & 0.87  & 0.88  & 0.88  & 0.88  & 0.88  & 0.88  \\
MSE      &  0.00 & 0.51  & 0.26 & 0.32  & 0.37& 0.48& 0.84& 2.03& 5.65&15.10 & 25.43 & 23.70 & 21.89 & 20.69 & 20.49 & 20.03 & 20.87 \\ \bottomrule
\end{tabular}%
}
\caption{Influence of Training Iterations}
\label{tab:iter}
\end{table*}

@@

\subsection{Datasets and Implementation Details}

We use SiamFC++ as our base tracker, and the backbone Siamese network adopts GoogLeNet.
We implement our our approach in Pytorch and train our perturbations using 3 GTX 1080Ti GPUs.
We adopt GOT-10k \cite{GOT-10k}, COCO \cite{COCO}, ILSVRC-VID \cite{VID} and LaSOT \cite{LaSOT} and our training set.
We train the perturbations for 32768 iterations with a minibatch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and the learning rate of the adversarial patch is $\epsilon_2 = 0.5$.
We generate training samples following the strategy in SiamFC++.
During the training and the testing phase, the size of the template image is set to $127\times 127\times 3$, and the size of the search image is set to $303\times 303\times 3$.
In equ. ?, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005, \sigma=1e-5$.
\textbf{Datasets} We evaluate our universal perturbations on several tracking datasets: OTB2015 \cite{OTB}, GOT-10k Val \cite{GOT-10k}, and LaSOT \cite{LaSOT}.

@@

\subsection{Generating the Fake Trajectory}

@@

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{cc|ccc}
\toprule
\multicolumn{2}{c|}{Backbone}                                                     & GoogLeNet & AlexNet & ShuffleNet    \\
\midrule
\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Perturbed\\Videos \end{tabular}} & AO (FGT)& 0.818     & 0.572   & 0.135 \\
                                                                            & SR (FGT)& 0.890     & 0.640   & 0.134 \\
\cmidrule{2-5}
                                                                            & AO (GT) & 0.035     & 0.196   & 0.554\\
                                                                            & SR (GT) & 0.023     & 0.227   & 0.656\\
\midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Clean\\Videos \end{tabular}}     & AO (GT) & 0.760     & 0.720   & 0.766         \\
                                                                            & SR (GT) & 0.897     & 0.850   & 0.888         \\
\bottomrule
\end{tabular}
}
\caption{Different backbone}
\end{table}

@@

\subsection{Generating Fake Trajectories}

>>>>

\begin{table*}
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{c|ccccccccccccccccc}
\toprule
Iterations &  0    &  1    &  2    &  4    & 8   & 16  & 32  & 64  & 128 & 256  & 512   & 1024  & 2048  & 4096  & 8192  & 16384 & 32768 \\ \midrule
AO (Fake Trajectory)   & 0.004 & 0.002 &0.002 & 0.002 &0.002&0.002&0.003&0.007&0.042& 0.299& 0.668 & 0.746 & 0.781 & 0.798 & 0.820 & 0.821 & 0.818 \\
SR (FGT) & 0.000 & 0.000 &0.000 & 0.000 &0.000&0.000&0.001&0.005&0.044& 0.335& 0.749 & 0.822 & 0.855 & 0.872 & 0.895 & 0.897 & 0.890 \\ \midrule
AO (GT)    &  0.760& 0.757 &0.756 & 0.757 &0.757&0.758&0.759&0.753&0.720& 0.474& 0.150 & 0.095 & 0.071 & 0.041 & 0.032 & 0.032 & 0.035 \\
SR (GT) &  0.897& 0.894 &0.891 & 0.893 &0.891&0.893&0.896&0.888&0.852& 0.559& 0.164 & 0.098 & 0.066 & 0.031 & 0.021 & 0.022 & 0.023 \\ \midrule
SSIM     &  1.00 & 1.00  & 1.00 & 1.00  &1.00 &0.99 & 0.99& 0.97& 0.93& 0.86 & 0.86  & 0.87  & 0.88  & 0.88  & 0.88  & 0.88  & 0.88  \\
MSE      &  0.00 & 0.51  & 0.26 & 0.32  & 0.37& 0.48& 0.84& 2.03& 5.65&15.10 & 25.43 & 23.70 & 21.89 & 20.69 & 20.49 & 20.03 & 20.87 \\ \bottomrule
\end{tabular}%
}
\caption{Influence of Training Iterations}
\label{tab:iter}
\end{table*}

@@

\subsection{Setting}

\subsubsection{Implementation Details}

We use SiamFC++ as our base tracker, and the backbone Siamese network adopts GoogLeNet.
We implement our our approach in Pytorch and train our perturbations using 3 GTX 1080Ti GPUs.
We adopt GOT-10k \cite{GOT-10k}, COCO \cite{COCO}, ILSVRC-VID \cite{VID} and LaSOT \cite{LaSOT} and our training set.
We train the perturbations for 32768 iterations with a minibatch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and the learning rate of the adversarial patch is $\epsilon_2 = 0.5$.
We generate training samples following the strategy in SiamFC++.
During the training and the testing phase, the size of the template image is set to $127\times 127\times 3$, and the size of the search image is set to $303\times 303\times 3$.
In equ. ?, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005, \sigma=1e-5$.

\subsubsection{Datasets}
We evaluate our universal perturbations on several tracking datasets: OTB2015 \cite{OTB}, GOT-10k Val \cite{GOT-10k}, and LaSOT \cite{LaSOT}.

@@

\subsubsection{Generating the Fake Trajectory}

@@

\begin{table}[ht]
\centering
\caption{Different backbone}
\begin{tabular}{c|cc|cc|cc} 
\toprule
\multirow{3}{*}{Backbone} & \multicolumn{2}{c|}{Clean Videos}    & \multicolumn{4}{c}{Perturbed Videos}                                        \\ 
\cmidrule{2-7}
                          & \multicolumn{2}{c|}{Real Trajectory} & \multicolumn{2}{c|}{Real Trajectory} & \multicolumn{2}{c}{Fake Trajectory}  \\ 
\cmidrule{2-7}
                          & AO    & SR                           & AO    & SR                           & AO    & SR                           \\ 
\midrule
GoogLeNet                 & 0.760 & 0.897                        & 0.035 & 0.023                        & 0.818 & 0.890                        \\
AlexNet                   & 0.720 & 0.850                        & 0.196 & 0.227                        & 0.572 & 0.640                        \\
ShuffleNet                & 0.766 & 0.888                        & 0.554 & 0.656                        & 0.135 & 0.134                        \\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Experiments}

\subsubsection{Targeted Attack Evaluation}

Two kinds of videos: the clean videos and the perturbed videos.
Two kinds of trajectories: the real trajectory and the fake trajectory.
So 4 combine: the clean videos + the real trajectory: the original result.
the perturbed video + the real trajectory: bad is good.
The perturbed video + the fake trajectory: high is good.
We hope that the attacked videos will have higher indicators on false trajectories and lower indicators on real trajectories.

\subsubsection{Generating Fake Trajectories}
